Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-15 paper.tex
cut update

\end{abstract}

\section{Introduction}\label{introduction}

@@

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are organised as the following: Sect. \ref{relatedWork} provides related works in the semantic web service composition; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model, proposed weighted graphs as solution presention and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents and analyses the experiment; Sect. \ref{conclusion} concludes our work.

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two. A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined in \cite{wu1994verbs}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$. However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most available semantic web services, as it takes huge cost and time for the domain experts to establish required ontology. In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation. However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.

\section{Problem Description}\label{problemDes}

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.

>>>>

\end{abstract}
\vspace{-0.8cm}
\section{Introduction}\label{introduction}

@@

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}
\vspace{-0.8cm}
\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two. A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description and Least common subsume are required to be pre-calculated. Therefore, the quality of the semantic link is estimated as quality of matching types associated with their corresponding quality of Common Description rate. However, the weakness of semantic link quality is that calculation requires well and completely defined ontology in class, class axioms and properties. This makes it difficult to measure semantic matchmaking quality as it takes huge cost and time for the domain experts to establish required ontology. In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation. However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
\vspace{-0.5cm}
\section{Problem Description}\label{problemDes}

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.
\vspace{-0.1cm}
